Efficient Feasibility Checking Algorithm of Photovoltaic Array Reconfiguration

### 2019-12-17 Journal-Photovoltaic/manuscript.tex
Zhao push @ 2019-12-17 16-59-41

\textbf{(Feasibility 1)}\footnote{In \cite{Orozco-Gutierrez2016}, only the case of $n=2$ is considered, and we extended the condition to general $n$. }
For each $n$-th highest current level $I_{n}$ in a current sequence for strings,
it is required that the number of active modules in a configuration is $N(I_{n}) / n$ or less, where $N(I)$ is the total number of active modules for a current level $I$. 
The maximum number $M$ of active modules for a PV array is given as
\begin{equation}
    M=\mbox{min}\begin{Bmatrix}
N(I),\frac{N(I_2)}{2},\frac{N(I_3)}{3},\cdots,\frac{N(I_{n})}{n}
\end{Bmatrix}.
\label{eq:1}
\end{equation}
Thus, approximated power $P$ can be calculated as follow.
\begin{equation}
\label{eq:2}
P=\sum{I_{n}}\times M \times \Bar{V}_{mpp}
\end{equation}

@@

\section{Feasibility}
From Orozco $et$ $al.$ method, to complete reconfiguration, we need to assign panels into strings to realize a candidate configuration.
For example, consider a candidate configuration for a current sequence (2.5A, 2.5A) with 3 active modules per string as shown in Table~\ref{tab:power-matrix}

\begin{table*}[t]
  \caption{}
  \centerline{APPROXIMATED POWER}
  \vskip5pt
\label{tab:power-matrix}
\centering
\begin{tabular}{c|rrrrrrrrrrr}
\hline\hline	
\# modules & 	\multicolumn{10}{c}{currents sequence for strings (A)} \\ 																
per string		&	\multicolumn{1}{c}{(3,3)}	&	\multicolumn{1}{c}{(3,2.5)}	&	\multicolumn{1}{c}{(3,1.5)}	&	\multicolumn{1}{c}{(3,0.5)}	&	\multicolumn{1}{c}{(2.5,2.5)}	&	\multicolumn{1}{c}{(2.5,1.5)}	&	\multicolumn{1}{c}{(2.5,0.5)}	&	\multicolumn{1}{c}{(1.5,1.5)}	&	\multicolumn{1}{c}{(1.5,0.5)}	&	\multicolumn{1}{c}{(0.5,0.5)}	\\ \hline
	1	&	120W	&	110W	&	90W	&	70W	&	100W	&	80W	&	60W	&	60W	&	40W	&	20W	\\ \hline
	2	&	-	&	220W	&	180W	&	140W	&	200W	&	160W	&	120W	&	120W	&	80W	&	40W	\\ \hline	3	&	-	&\textbf{330W}&	270W	&	210W	&	\textbf{300W}	&	240W	&	180W	&	180W	&	120W	&	60W	\\ \hline
4	&	-	&	-	&	-	&	-	&	-	&	\textbf{320W}	&	240W	&	240W	&	160W	&	80W	\\ \hline
	 5	&	-	&	-	&	-	&	-	&	-	&	-	&	\textbf{300W}	&	-	&	200W	&	100W	\\ \hline
	6	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	240W	&	120W	\\ \hline
\end{tabular}
\end{table*}
\section{Algorithm to identify feasibility}\label{sec:algor-ident-feas}
\subsection{Feasibility problem}\label{sec:feasibility-problem}
\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
\subsection{Algorithm}\label{sec:algorithm}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.

@@

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\section*{Temp}
It is well known that mismatch due to partial shading, soiling, or ageing causes significant losses
in the energy yield of photovoltaic (PV) systems [1,2]. Furthermore, mismatches may hinder operation
of maximum power point (MPP) tracking algorithms, especially if the power versus output voltage
characteristic becomes nonconvex [3]. It has also been shown that, even with commonly used bypass
diodes, mismatched cells may become reverse-biased and dissipate power, producing an undesired
cell temperature rise or hot spot [4,5]. This may lead to accelerated ageing and reduced reliability of
the PV system

>>>>

\textbf{(Feasibility 1)}\footnote{In \cite{Orozco-Gutierrez2016}, only the case of $n=2$ is considered, and we extended the condition to general $n$. }
For each $n$-th highest current level $I_{n}$ in a current sequence $Q$ for strings,
it is required that the number of active modules in a configuration is $N(I_{n}) / n$ or less, where $N(I)$ is the total number of active modules for a current level $I$. 
The maximum number $M$ of active modules for a PV array is given as
\begin{equation}
    M=\mbox{min}\begin{Bmatrix}
N(I),\frac{N(I_2)}{2},\frac{N(I_3)}{3},\cdots,\frac{N(I_{n})}{n}
\end{Bmatrix}.
\label{eq:1}
\end{equation}
Thus, approximated power $P$ can be calculated as follow.
\begin{equation}
\label{eq:2}
P=\sum{Q}\times M \times \Bar{V}_{mpp}
\end{equation}

@@

\section{Feasibility}

\begin{table*}[t]
  \caption{}
  \centerline{APPROXIMATED POWER}
  \vskip5pt
\label{tab:power-matrix}
\centering
\begin{tabular}{c|rrrrrrrrrrr}
\hline\hline	
\# modules & 	\multicolumn{10}{c}{currents sequence for strings (A)} \\ 																
per string		&	\multicolumn{1}{c}{(3,3)}	&	\multicolumn{1}{c}{(3,2.5)}	&	\multicolumn{1}{c}{(3,1.5)}	&	\multicolumn{1}{c}{(3,0.5)}	&	\multicolumn{1}{c}{(2.5,2.5)}	&	\multicolumn{1}{c}{(2.5,1.5)}	&	\multicolumn{1}{c}{(2.5,0.5)}	&	\multicolumn{1}{c}{(1.5,1.5)}	&	\multicolumn{1}{c}{(1.5,0.5)}	&	\multicolumn{1}{c}{(0.5,0.5)}	\\ \hline
	1	&	120W	&	110W	&	90W	&	70W	&	100W	&	80W	&	60W	&	60W	&	40W	&	20W	\\ \hline
	2	&	-	&	220W	&	180W	&	140W	&	200W	&	160W	&	120W	&	120W	&	80W	&	40W	\\ \hline	3	&	-	&\textbf{330W}&	270W	&	210W	&	\textbf{300W}	&	240W	&	180W	&	180W	&	120W	&	60W	\\ \hline
4	&	-	&	-	&	-	&	-	&	-	&	\textbf{320W}	&	240W	&	240W	&	160W	&	80W	\\ \hline
	 5	&	-	&	-	&	-	&	-	&	-	&	-	&	\textbf{300W}	&	-	&	200W	&	100W	\\ \hline
	6	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	-	&	240W	&	120W	\\ \hline
\end{tabular}
\end{table*}

From Orozco $et$ $al.$ method, to complete reconfiguration, we need to assign panels into strings to realize a candidate configuration.
For example, consider a candidate configuration for a current sequence (2.5A, 2.5A) with 3 active modules per string as shown in Table~\ref{tab:power-matrix}
It can be realized by assigning panel P2 to the first string and panel P1 and P4 to the second string as shown in Figure~\ref{fig:feasibleassign}.
However, for another current sequence (2.5A, 1.5A), there is no feasible assignment for 4 active modules per string, even though this configuration is listed in Table~\ref{tab:power-matrix} by method in\cite{Orozco-Gutierrez2016}.
It is same for a configuration candidate with current sequence (3A, 2.5A) for 3 active modules per string.
That is, the condition \textbf{Feasibility 1} is necessary but not sufficient to give an actual feasibility result.

For a PV array $A$ with $s$ strings, let $M_{A,i}(I)$ denotes the number of modules that can be activated with a current level $I$ in the $i$-th string.
Let $Q = (Q_1,Q_2,\dots,Q_s)$ be the sequence of current required for strings.
We define the feasibility as follows: A sequence of current $Q$ is feasible with $m$ modules if and only if it is possible to form a PV array $A$ such that
\begin{equation}
  M_{A,i}(Q_i)\geq m
  \label{eq:3}
\end{equation}
holds for each string $i$ (1$\leq i \leq s$).

\begin{figure}[htbp]
    \centering
    \includegraphics[width=\linewidth]{fig/feasible-configuration.pdf}
    \caption{Feasible configuration for a current sequence (2.5A, 2.5A) with 3 active modules.}
    \label{fig:feasibleassign}
\end{figure}

\section{Algorithm to identify feasibility}\label{sec:algor-ident-feas}
\subsection{Feasibility problem}\label{sec:feasibility-problem}
In this section, we introduce an algorithm to identify feasibility for a configuration.
First we will formulate the feasibility problem that identifies the feasibility for a given current sequence and the number of active modules per string as follows.

\textit{Definition 1} (\textit{Feasibility Problem}):\\
\textbf{Input}: Information of MPPs (approximated values), a current sequence $Q$, the number of $m$ of active modules per-string.\\
%\newline
\textbf{Output}: Whether $Q$ with $m$ modules is feasible or not.

\subsection{Outline of the algorithm}\label{sec:outline-algorithm}
\subsection{Algorithm}\label{sec:algorithm}
\section{Experiment Results}\label{sec:experiment-results}
\section{Conclusion}\label{sec:conclusion}
The conclusion goes here.

@@

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
% \section*{Temp}
% It is well known that mismatch due to partial shading, soiling, or ageing causes significant losses
% in the energy yield of photovoltaic (PV) systems [1,2]. Furthermore, mismatches may hinder operation
% of maximum power point (MPP) tracking algorithms, especially if the power versus output voltage
% characteristic becomes nonconvex [3]. It has also been shown that, even with commonly used bypass
% diodes, mismatched cells may become reverse-biased and dissipate power, producing an undesired
% cell temperature rise or hot spot [4,5]. This may lead to accelerated ageing and reduced reliability of
% the PV system
